Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-12 doc/PRF2022/PRF_main.tex
peter added captions

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-2}

@@

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}asdf}
\end{figure}
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively. 
In both cases, $\dot \gamma$ is the shear rate.
To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
 where shear rates range over 100--2000 s$^{-1}$ \cite{Cho2011}.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}}
\end{figure}
\subsection{Rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this was is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

>>>>

%% ***A*** Start of file apstemplate.tex ****** %
%%
%%
%%   This file is part of the APS files in the REVTeX 4.2 distribution.
%%   Version 4.2a of REVTeX, January, 2015
%%
%%
%%   Copyright (c) 2015 The American Physical Society.
%%
%%   See the REVTeX 4 README file for restrictions and more information.
%%
%
% This is a template for producing manuscripts for use with REVTEX 4.2
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.
%
% Group addresses by affiliation; use superscriptaddress for long
% author lists, or if there are many overlapping affiliations.
% For Phys. Rev. appearance, change preprint to twocolumn.
% Choose pra, prb, prc, prd, pre, prl, prstab, prstper, or rmp for journal
%  Add 'draft' option to mark overfull boxes with black boxes
%  Add 'showkeys' option to make keywords appear
%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-2}
\documentclass[prb,preprint,showpacs,preprintnumbers,amsmath,amssymb,longbibliography]{revtex4-1}

@@

\section{Results and Discussion}
\label{sec:results}
\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{S2ESummary.pdf}
\end{center}
\caption{\label{fig:s2esummary}
Panel (a)-(b) show the average strain increase in percentage of vesicle, bilayer, multilamellar, and striated JP structures under a shear flow and a TG flow, respectively.
Panel (c)-(d) show the average alignment of four JP structures under a shear flow and a TG flow, respectively. 
Each snapshot of panels (e)-(l) contains the configurations of the JP structure using a specific type of boundary bondition without ruptures and the backgroud curves indicate the streamlines.}
\end{figure}
%
We subjected the Type I, II, and III JP phases to background flows and measured 
their material response.  The background flows were a shear flow
\begin{equation}
\label{eq:sh_flow}
\uu_\infty^{\text{sh}}(\xx) = 
\dot\gamma (\ee_y \cdot \mathbf{x})\ee_x,
\end{equation}
and a Taylor-Green (TG) flow
\begin{equation}
\label{eq:tg_flow}
\uu_\infty^{\text{TG}}(\xx) = 
\lambda \dot \gamma \left(
-\cos(\ee_x\cdot\xx/\lambda)\sin(\ee_y\cdot\xx/\lambda)\ee_x
+\sin(\ee_x\cdot\xx/\lambda)\cos(\ee_y\cdot\xx/\lambda)\ee_y\right),
\end{equation}
where the orthonormal vectors $\ee_x$ and $\ee_y$ are the horizontal
and vertical directions, respectively. 
In both cases, $\dot \gamma$ is the shear rate.
To obtain a range for $\dot \gamma$, 
consider the capillary number 
\begin{equation}
\label{eq:capillary}
C_a = \frac{\mu \dot \gamma R^3}{\kappa}
\end{equation}
where $R = 10$ nm and $\kappa = 20\;\kbt$ are 
the characteristic phase sample radius 
and bending rigidity, respectively. 
That is, $\kappa$ gives the elastic stress 
for restoring the phase-sample shape.
Shear stress overcomes elastic stress   
when $C_a > 1$ and this yields 
$\dot \gamma > 2 \cdot 10^{-2}$ ns$^{-1} = 2 \cdot 10^6$ s.
Thus our values for $\dot \gamma$ range between 
$0$ ns$^{-1}$ corresponding to quiescent flow
up to $0.2$ ns$^{-1}$ capable of rupturing the sample. 
Such shear rates are compatible with molecular dynamics 
simulation \cite{Brandner2019}, those for large unilamellar vesicles (LUV),
\cite{Bernard2005ShearinducedPA} and shearing in blood capillary vessels 
 where shear rates range over 100--2000 s$^{-1}$ \cite{Cho2011}.

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{FSummary.pdf}
\end{center}
\caption{\label{fig:fsummary}
The change of average free energy versus shear rates for shear flow and TG flow simulation results are plotted in panels (a)-(b). Panel (c) shows the relationships between the changes of the free energy as mean displacements of JP increases and the types of boundary conditions. All data points are fitted by quadratic functions and represented in dashed curves.}
\end{figure}

@@

\begin{figure}[t]
\begin{center}
\includegraphics[width=\textwidth]{RheologySummary.pdf}
\end{center}
\caption{\label{fig:rheologysummary}
Rheology in Type I, II, and III. Panel (a) shows that unilamellar JP bilayer and vesicle both behave close to a Newtonian fluid. Panel (b) provides that the multilamellar phase shows a near shear thinning behaviour. A pseudoplastic behaviour of deformation in striated JP structure is shown in panel (c). }
\end{figure}
\subsection{Rheology}
So far, we have considered static material properties, namely
constant strains maintained by an external force provided by   
background flow. Now we consider dynamic material properties.
Specifically, we look at the strain rate 
\begin{equation}
\label{eq:strainrate}
\dot E = \left(\frac{1}{T} \int_0^T \left|\frac{dE}{dt}\right|^2 \, \dif t \right)^{1/2}.
\end{equation}
The reason for defining $\dot E$ in this was is that 
the shear flow $\uu_{\infty}^{\text{sh}}$
simulations correspond to a complex fluid within a drag plate
rheometer where the shear stress is set by $\mu \dot\gamma$  
and the observed, sample shear rate is $\dot E$. 
The definitions carry over to the TG flow case directly. 
Also, as a practical consideration,
the rotation of non-isotropic JP phases in the background 
flow leads to oscillation in the strain time courses 
making systematic fitting challenging (see 
Supplementary Material Figures \ref{fig:veshraw}--\ref{fig:sttgraw}). 
The integral in \eqref{eq:strainrate} averages out these oscillations
and gives physically meaningful values.

### 2023-03-12 doc/PRF2022/Supplementary.tex
Results and SM updated
peter working on tasks
peter added captions

  \noindent 
  Collective behavior of Janus Particles Suspended in a Viscous Fluid}\\

@@

>>>>

  \noindent 
 Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows}\\

@@

\section{Raw Data}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/VeShRaw.pdf}
\end{center}
\caption{A Vesicle under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:veshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/ULShRaw.pdf}
\end{center}
\caption{A unilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.013\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:ulshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLShRaw.pdf}
\end{center}
\caption{A multilamellar JP structure under a shear flow with choices of shear rates $\dot\gamma=0.025\sim0.075$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:mlshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StShRaw.pdf}
\end{center}
\caption{A striated JP structure under a shear flow with choices of shear rates $\dot\gamma=0.01\sim0.07$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:stshraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/VeTGRaw.pdf}
\end{center}
\caption{A vesicle JP structure under a TG flow with choices of shear rates $\dot\gamma=0.005\sim0.044$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:vetgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/ULTGRaw.pdf}
\end{center}
\caption{A unilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.013\sim0.05$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:ultgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/MLTGRaw.pdf}
\end{center}
\caption{A multilamellar JP structure under a TG flow with choices of shear rates $\dot\gamma=0.025\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:mltgraw}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{SMFigures/StTGRaw.pdf}
\end{center}
\caption{A striated JP structure under a TG flow with choices of shear rates $\dot\gamma=0.01\sim0.069$. The change in free energy $F$ is plotted in panel (a). Panel (b) shows the scalar order parameter $S_2$ over time $t$. Panel (c) plots the change of strain parameter $E$ in percentage over time $t$. }
\label{fig:mltgraw}
\label{fig:sttgraw}
\end{figure}
